\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-03-08 paper/wireframe/wireframe.tex
added physical section

>>>>

\subsection{Physical Analysis}
\begin{itemize}
    \item Search the lock for potential physical bypass attacks 
    \item Search for issues with the magnetic anti-tamper switch
    \item Search the lock for easy access to Wiegand protocol leads
    \item Search for potential areas of destructive entry
\end{itemize}

Enterprise locks often have many potential types of issues from the perspective of a physical attack.  The authors expect to find potential implementation errors in areas such as the configuration of the anti-tamper switch, the location of the connectors to the Wiegand network, or access to the locking motor from within the device.  In order to detect these issues, the authors will analyze the lock from the perspective of a typical wall-mounted installation.  From there, the authors will look into various ways to both undestructively, and destructively trigger an unlock.  In a physical test, a vulnerability can take a lot of different forms.
